pediatricResults

### 2021-11-04 metanalysis_visualization/pedsResults.Rmd
adding general trend meta analysis

---
title: "pediatricResults"
author: "aGutierrezSacristan"
date: "10/26/2021"
output: html_document
---
```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta")
paket(listOfPackages)
```

@@

```{r}
outputDir <- "./output/"
outputFiles <- list.files( path = outputDir, pattern = ".RData")
```

Put all the aggregate counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
  }else{
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, table1, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, length_hospitalisation_values)
}
```

@@

>>>>

---
title: "pediatricResults"
author: "aGutierrezSacristan"
date: "10/26/2021"
output: html_document
---
```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis")
paket(listOfPackages)
```

@@

```{r}
outputDir <- "../output/"
outputFiles <- list.files( path = outputDir, pattern = "\\.RData")
getwd()
```

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
  }else{
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
  }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, table1, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, length_hospitalisation_values)
}
```

@@

#### Meta-analysis of temporal trends

```{r}
## Estimate sampling variances
meta_df <- ratios_patients_with_without_psy_all
meta_df$time <- as.numeric(as.factor(meta_df$time_p))
##### Sampling model 
trend_model <- "percentage ~ period * time"
trends <- meta_df %>% 
  group_by(siteid) %>% 
  group_modify( ~ broom::tidy(lm(as.formula(trend_model), data = .x))) %>%
  filter(term == c("periodduring_pandemic:time")) %>% 
  mutate(variance = std.error * std.error) %>% 
  select(siteid, estimate, variance)

```{r}
meta_df$sampling_variances
## Fixed Effect model

model_meta <- metafor::rma(yi = estimate, 
             vi = variance,
             measure = "GEN",
  data = trends)

model_meta %>% 
  broom::tidy()

predict(model_meta)
fitted(model_meta)

metafor::forest(model_meta,
                atransf=exp,
                slab = trends$siteid,
                header="Sites",
                mlab="Overall temporal trend")
```
